The effect of commen network problems on students academic performance in an elearning-Environment \thanks{Supported by Goethe University Frankfurt a. Main}

### 2021-07-08 Draft.tex
Very close to done

\renewcommand\UrlFont{\color{blue}\rmfamily}

@@

We tried to focus on the most frequent issues we faced in our experience of browsing 
on different platforms, which are defined by HTTP-status-codes, like 400 (Bad Request), 401 
(Unauthorized), 403 (Forbidden), 404 (Not Found), 408 (Request Timeout), as mostly being 'client-errors'.\\\\
\newpage
\section{Materials and Methodes}
\subsection{Participants}
The participants are students of the end of the 4 grade and consist of two groups the control group [CG] and
the test group [TG]. Each group is made up by 50 girls and 50 boys for a total of 200 participants.
It should be ensured that both groups prior to the experiment perform academicly similar, if not a
comparison post experiment will be difficult. Students of the 5th grade have the benefit of the
already finished primary school. Which ensures experience in simple problem solving and
reading comprehension. Futhermore in 4th grade we can still observe all academic capabilitys
since the division of students happens in 5th grade.

\subsection{Preperations}
The experiment was conducted by creating a software implementing Fig.~\ref{fig1}.
This software allowed the tracking of {\itshape technical problems} introduced by
the software itself as well as the points and answers scored by each participant.
Additianaly a room with an adequat number of computers with a fiber-connection
to the server are needed, to rule out uncontrolled network problems.
Half of the cumputers are manipulated and simulate the network problems with the
use of the software.

@@

\section{Discussion}
The collected data is very clear. Network problems do not affect students academic performance
in a statistically firm manner.\\\\

The results can not be transposed on younger students.
Since younger students might be unable to read properly or lack experience with problem solving
in general. Futhermore can the data not be used to make an estimate for students with disabilitys.
However the performance of older students should be similar to the tested students.\\\\

The study can make a general statement on network problems. However not all possible
problems are simulated. It is possible that a problem exists that does affect the academic performance of
students significantly. Futhermore designflaws of the eLearning-Environment
or limited to no access to a computer are problems that are overlooked or ignored. These problems
require additional studys.
\section{Conclusion}

\section{Refernces}
\end{document}

>>>>

%\renewcommand\UrlFont{\color{blue}\rmfamily}

@@

We tried to focus on the most frequent issues we faced in our experience of browsing 
on different platforms, which are defined by HTTP-status-codes, like 400 (Bad Request), 401 
(Unauthorized), 403 (Forbidden), 404 (Not Found), 408 (Request Timeout), as mostly being 'client-errors'.\\\\
\newpage
\section{Materials and Methodes}
\subsection{Summary}
To which extend do commen networks problems in an eLearning-Environment
influence the academic performance of students. This information can be used to
re-evaluate the eLearning-Environment.

\subsection{Participants}
The participants are students of the end of the 4 grade and consist of two groups the control group [CG] and
the test group [TG]. Each group is made up by 50 girls and 50 boys for a total of 200 participants.
It should be ensured that both groups prior to the experiment perform academicly similar, if not a
comparison post experiment will be difficult. Students of the end of the 4th grade have the benefit of the
already finished primary school. Which ensures experience in simple problem solving and
reading comprehension. Futhermore in 4th grade we can still observe all academic capabilitys
since the division of students happens in 5th grade. Also primary school has the least differences
in the curriculum between the federal stats.

\subsection{Preperations}
The experiment was conducted by creating a software implementing Fig.~\ref{fig1}.
This software\cite{ref_soft} allowed the tracking of {\itshape technical problems} introduced by
the software itself as well as the points and answers scored by each participant.
A maximum of 100 points could be scored, these were needed to evaluate the performance of
the students. Anymore name, gender, age, email, username and password were collected.
These parameters were used to identify students and for futher analysis.
Other solutions which involed already existing softwaresuits were abandon due to lack
of customization.Additianaly a room with an adequat number of computers with a fiber-connection
to the server are needed, to rule out uncontrolled network problems.
Half of the cumputers are manipulated and simulate the network problems with the
use of the software.

\subsection{}

@@

\section{Discussion}
The collected data is very clear. Network problems do not affect students academic performance
in a statistically firm manner.

The results can not be transposed on younger students.
Since younger students might be unable to read properly or lack experience with problem solving
in general. Futhermore can the data not be used to make an estimate for students with disabilitys.
However the performance of older students should be similar to the tested students.

The study can make a general statement on network problems. However not all possible
problems are simulated. It is possible that a problem exists that does affect the academic performance of
students significantly. Also longterm effects can not be discoverd by this study since it is very time limited.
Futhermore designflaws of the eLearning-Environment or limited to no access to a computer are problems that
are overlooked or ignored. These problems require additional studys.
\section{Conclusion}
In this paper we could clearly see the impact of platform-issues on the students performance in an 
exam-scenario and it is not significant. There might still be certain aspect of long-term-effects,
which we couldn't simulate due to our test setup, because there was a slight worsening happening 
when comparing our outcomes. It would be very interesting to see, how much significance such things 
like errors will show  in a long run with more variables included.
\section{Refernces}
\begin{thebibliography}{8}
    \bibitem{ref_soft}
    Github, \url{https://github.com/UebeI2lauf/insertcreativeName/tree/main/code}. Last accessed 8 Jul 2021
    \end{thebibliography}
\end{document}
